### 2021-02-25 text/draft.tex
clean up

In order to determine how well the sample data set represents the raw
Edoc data, a one-sample chi-square test was conducted on each selection
data field (see Parke 2013, chap. 1). The results indicate that the
sample data proportions of items are significantly different from the
raw Edoc data per department (see Figure 1 for more details).

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data (\(N\) = 68'345) per department. Data field
\texttt{abstract}: \(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data
field \texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285,
\(p < 0.001\); data field \texttt{keywords}: \(\chi^2 (df=9) =\)
2'314.533, \(p < 0.001\). The data foundation is available at
\texttt{/edoc/analysis} and the chi-square statistic can be calculated
by calling
\texttt{\_Analysis.get\_\textasciitilde{}\textasciitilde{}\textasciitilde{}\textasciitilde{}chi\_square\_fit}.}
\end{figure}

The sample data set is hence not representative of the raw Edoc data.
This is not surprising since its construction is strongly biased. This
bias has the effect that the sample data set is significantly skewed
towards English journal publications in the sciences, medicine and
economics from the 21st century (see Figure 2 for more details). The
upshot of this analysis is that the humanities are underrepresented in
the sample data set. Therefore, any results with respect to the quality
of machine indexing discussed below might not be applicable to the
humanities.

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276\$, \(p < 0.001\)) from the 21st (data
field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\))
century as compared to the raw Edoc data (\(N\) = 68'345). The data
foundation is available at \texttt{/edoc/analysis} and the chi-square
statistic can be calculated by calling
\texttt{\_Analysis.chi\_square\_fit}.}
\end{figure}

@@

The median number of keywords for an item in the sample data set is 6
with an \(IQR\) of 4 (\(min = 0\), \(Q1 = 4\), \(M = 6\), \(Q3 = 8\),
\(max = 87\)). Of course, items in the sample data set with a number of
keywords below the first and above the third quartile are highly suspect
from a qualitative point of view: when it comes to subject indexing,
some terms are required, but more is usually worse {[}!! source{]}.
Items with too few or too many keywords will be discussed in more detail
in section \protect\hyperlink{assessment}{section Assessment}

@@

Let us now turn to the evaluation of the reconciliation: how many of the
suggestions were correct? This question was answered via random
sampling. The random sample (\(n=500\)) was created by calling
\texttt{\_Analysis.make\_random\_sample} on
\texttt{/keywords/reference\_keywords\_master.json}; it is available at
\texttt{/analysis/random\_keywords.json}. The sample was then imported
into OpenRefine and the judgement (1 for correct, 0 for incorrect) of
the manual verification was recorded in the column
\texttt{verification}. The data was then exported and is available at
\texttt{/analysis/random\_keywords\_verified.csv}.

@@

>>>>

In order to determine how well the sample data set represents the raw
Edoc data, a one-sample \(\chi^2\) goodnes of fit test was conducted on
each selection data field (following Parke 2013, chap. 1). The results
indicate that the sample data proportions of items are significantly
different from the raw Edoc data per department (see Figure 1 for more
details).

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data per department. Data field \texttt{abstract}:
\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
The data foundation is available at
\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
the data foundation files.}
\end{figure}

The sample data set is hence not representative of the raw Edoc data.
This is not surprising since its construction is strongly biased. This
bias has the effect that the sample data set is significantly skewed
towards English journal publications in the sciences, medicine and
economics from the 21st century (again, this is shown by a one-sample
\(\chi^2\) goodness of fit test, see Figure 2 for more details). The
upshot of this analysis is that the humanities are underrepresented in
the sample data set. Therefore, any results with respect to the quality
of machine indexing discussed below might not be applicable to the
humanities.

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st (data field
\texttt{date}: \(\chi^2 (df=7) =\) 35'878.493, \(p < 0.001\)) century as
compared to the raw Edoc data. The data foundation is available at
\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
be calculated by calling \texttt{\_Analysis.get\_chi\_square\_fit} on
the data foundation files.}
\end{figure}

@@

The median number of keywords for an item in the sample data set is 6
with an IQR of 4 (min = 0, Q1 = 4, M = 6, Q3 = 8, max = 87). Of course,
items in the sample data set with a number of keywords below the first
and above the third quartile are highly suspect from a qualitative point
of view: when it comes to subject indexing, some terms are required, but
more is usually worse {[}!! source{]}. Items with too few or too many
keywords will be discussed in more detail in section
\protect\hyperlink{assessment}{section Assessment}

@@

Let us now turn to the evaluation of the reconciliation: how many of the
suggestions were correct? This question was answered via random sampling
(following Roth and Heidenreich 1993, 204--25). The random sample
(\(n=500\)) was created by calling
\texttt{\_Analysis.make\_random\_sample} on
\texttt{/keywords/reference\_keywords\_master.json}; it is available at
\texttt{/analysis/random\_keywords.json}. The sample was then imported
into OpenRefine and the judgement (1 for correct, 0 for incorrect) of
the manual verification was recorded in the column
\texttt{verification}. The data was then exported and is available at
\texttt{/analysis/random\_keywords\_verified.csv}.

@@

\leavevmode\hypertarget{ref-Roth.1993}{}%
Roth, Erwin, and Klaus Heidenreich. 1993. \emph{Sozialwissenschaftliche
Methoden: Lehr- Und Handbuch f{ü}r Forschung Und Praxis}. 3., v{ö}llig
{ü}berarbeitete und erweiterte Auflage. M{ü}nchen {[}etc.{]}: {R.
Oldenbourg Verlag}.
